Deeply Integrating C11 Code Support into Isabelle/PIDE

### 2019-10-15 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse revision 5366

%
\begin{isabellebody}%
\setisabellecontext{paper}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimML
%
\endisadelimML
%
\isatagML
%
\endisatagML
{\isafoldML}%
%
\isadelimML
%
\endisadelimML
%
\begin{isamarkuptitle*}%
[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Deeply Integrating C11 Code Support into Isabelle/PIDE%
\end{isamarkuptitle*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {bu},type = {scholarly_paper.author}, args={label = {bu},type = {scholarly_paper.author}, scholarly_paper.author.email = {wolff@lri.fr}, scholarly_paper.author.affiliation = {LRI, Univ. Paris-Sud, CNRS, Université Paris-Saclay}, scholarly_paper.author.http_site = {https://www.lri.fr/~wolff/}, scholarly_paper.author.orcid = {}}]Burkhart Wolff%
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {abs},type = {scholarly_paper.abstract}, args={label = {abs},type = {scholarly_paper.abstract}, scholarly_paper.abstract.keywordlist = {{User Interface, Integrated Development, Program Verification, Shallow Embedding}}}]We present a framework for C code in C11 syntax deeply integrated into the Isabelle/PIDE
  development environment. Our framework provides an abstract interface for verification back-ends
  to be plugged-in independently. Thus, various techniques such as deductive program verification or
  white-box testing can be applied to the same source, which is part of an integrated PIDE document
  model. Semantic back-ends are free to choose the supported C fragment and its semantics. In
  particular, they can differ on the chosen memory model or the specification mechanism
  for framing conditions.

@@

\endinput
%:%32=54%:%
%:%36=61%:%
%:%40=67%:%
%:%41=68%:%
%:%42=69%:%
%:%43=70%:%
%:%44=71%:%
%:%45=72%:%
%:%46=73%:%
%:%47=74%:%
%:%48=75%:%
%:%49=76%:%
%:%50=77%:%
%:%51=78%:%
%:%52=79%:%
%:%53=80%:%
%:%54=81%:%
%:%55=82%:%
%:%56=83%:%
%:%57=84%:%
%:%58=85%:%
%:%62=88%:%
%:%66=90%:%
%:%67=91%:%
%:%68=92%:%
%:%69=93%:%
%:%70=94%:%
%:%71=95%:%
%:%72=96%:%
%:%73=97%:%
%:%74=98%:%
%:%75=99%:%
%:%76=100%:%
%:%77=101%:%
%:%78=102%:%
%:%79=103%:%
%:%80=104%:%
%:%81=105%:%
%:%82=106%:%
%:%83=107%:%
%:%84=108%:%
%:%85=109%:%
%:%86=110%:%
%:%87=111%:%
%:%88=112%:%
%:%89=113%:%
%:%90=114%:%
%:%91=115%:%
%:%92=116%:%
%:%93=117%:%
%:%94=118%:%
%:%95=119%:%
%:%96=120%:%
%:%97=121%:%
%:%98=122%:%
%:%99=123%:%
%:%100=124%:%
%:%101=125%:%
%:%102=126%:%
%:%103=127%:%
%:%104=128%:%
%:%105=129%:%
%:%109=147%:%
%:%113=149%:%
%:%114=150%:%
%:%115=151%:%
%:%116=152%:%
%:%117=153%:%
%:%118=154%:%
%:%119=155%:%
%:%120=156%:%
%:%121=157%:%
%:%122=158%:%
%:%126=169%:%
%:%127=170%:%
%:%128=171%:%
%:%129=172%:%
%:%130=173%:%
%:%131=174%:%
%:%132=175%:%
%:%133=176%:%
%:%137=179%:%
%:%141=181%:%
%:%142=182%:%
%:%143=183%:%
%:%144=184%:%
%:%145=185%:%
%:%146=186%:%
%:%147=187%:%
%:%148=188%:%
%:%149=189%:%
%:%153=193%:%
%:%157=196%:%
%:%161=200%:%
%:%162=201%:%
%:%163=202%:%
%:%164=203%:%
%:%165=204%:%
%:%166=205%:%
%:%167=206%:%
%:%168=207%:%
%:%169=208%:%
%:%170=209%:%
%:%171=210%:%
%:%172=211%:%
%:%173=212%:%
%:%174=213%:%
%:%175=214%:%
%:%176=215%:%
%:%177=216%:%
%:%178=217%:%
%:%179=218%:%
%:%180=219%:%
%:%189=221%:%
%:%201=223%:%
%:%202=224%:%
%:%203=225%:%
%:%204=226%:%
%:%205=227%:%
%:%206=228%:%
%:%207=229%:%
%:%208=230%:%
%:%209=231%:%
%:%210=232%:%
%:%211=233%:%
%:%212=234%:%
%:%213=235%:%
%:%214=236%:%
%:%215=237%:%
%:%216=238%:%
%:%217=239%:%
%:%218=240%:%
%:%219=241%:%
%:%220=242%:%
%:%221=243%:%
%:%222=244%:%
%:%223=245%:%
%:%224=246%:%
%:%225=247%:%
%:%226=248%:%
%:%227=249%:%
%:%228=250%:%
%:%229=251%:%
%:%230=252%:%
%:%231=253%:%
%:%232=254%:%
%:%233=255%:%
%:%234=256%:%
%:%235=257%:%
%:%236=258%:%
%:%237=259%:%
%:%238=260%:%
%:%239=261%:%
%:%240=262%:%
%:%241=263%:%
%:%242=264%:%
%:%243=265%:%
%:%244=266%:%
%:%245=267%:%
%:%246=268%:%
%:%247=269%:%
%:%248=270%:%
%:%249=271%:%
%:%250=272%:%
%:%251=273%:%
%:%252=274%:%
%:%253=275%:%
%:%254=276%:%
%:%254=277%:%
%:%255=278%:%
%:%256=279%:%
%:%257=280%:%
%:%258=281%:%
%:%259=282%:%
%:%260=283%:%
%:%261=284%:%
%:%262=285%:%
%:%263=286%:%
%:%272=291%:%
%:%284=294%:%
%:%285=295%:%
%:%286=296%:%
%:%287=297%:%
%:%288=298%:%
%:%289=299%:%
%:%290=300%:%
%:%291=301%:%
%:%292=302%:%
%:%293=303%:%
%:%294=304%:%
%:%295=305%:%
%:%296=306%:%
%:%297=307%:%
%:%298=308%:%
%:%299=309%:%
%:%300=310%:%
%:%301=311%:%
%:%302=312%:%
%:%303=313%:%
%:%304=314%:%
%:%305=315%:%
%:%306=316%:%
%:%307=317%:%
%:%311=320%:%
%:%315=323%:%
%:%316=324%:%
%:%317=325%:%
%:%318=326%:%
%:%319=327%:%
%:%320=328%:%
%:%321=329%:%
%:%322=330%:%
%:%323=331%:%
%:%324=332%:%
%:%325=333%:%
%:%326=334%:%
%:%327=335%:%
%:%328=336%:%
%:%329=337%:%
%:%330=338%:%
%:%331=339%:%
%:%332=340%:%
%:%333=341%:%
%:%334=342%:%
%:%335=343%:%
%:%339=347%:%
%:%343=363%:%
%:%347=364%:%
%:%348=365%:%
%:%350=366%:%
%:%351=367%:%
%:%356=370%:%
%:%357=371%:%
%:%358=372%:%
%:%359=373%:%
%:%360=374%:%
%:%361=375%:%
%:%365=377%:%
%:%366=378%:%
%:%367=379%:%
%:%368=380%:%
%:%369=381%:%
%:%370=382%:%
%:%371=383%:%
%:%372=384%:%
%:%373=385%:%
%:%374=386%:%
%:%375=387%:%
%:%379=390%:%
%:%380=391%:%
%:%381=392%:%
%:%382=393%:%
%:%383=394%:%
%:%387=397%:%
%:%391=399%:%
%:%392=400%:%
%:%393=401%:%
%:%394=402%:%
%:%395=403%:%
%:%399=432%:%
%:%403=433%:%
%:%404=434%:%
%:%405=435%:%
%:%406=436%:%
%:%407=437%:%
%:%408=438%:%
%:%412=440%:%
%:%413=441%:%
%:%414=442%:%
%:%415=443%:%
%:%416=444%:%
%:%420=445%:%
%:%421=446%:%
%:%423=447%:%
%:%424=448%:%
%:%426=449%:%
%:%431=456%:%
%:%432=457%:%
%:%433=458%:%
%:%433=459%:%
%:%434=460%:%
%:%435=461%:%
%:%436=462%:%
%:%437=463%:%
%:%438=464%:%
%:%439=465%:%
%:%440=466%:%
%:%449=468%:%
%:%461=470%:%
%:%462=471%:%
%:%463=472%:%
%:%464=473%:%
%:%465=474%:%
%:%466=475%:%
%:%467=476%:%
%:%468=477%:%
%:%469=478%:%
%:%469=479%:%
%:%470=480%:%
%:%471=481%:%
%:%472=482%:%
%:%473=483%:%
%:%474=484%:%
%:%483=486%:%
%:%495=488%:%
%:%496=489%:%
%:%497=490%:%
%:%498=491%:%
%:%499=492%:%
%:%500=493%:%
%:%501=494%:%
%:%510=496%:%
%:%522=498%:%
%:%523=499%:%
%:%524=500%:%
%:%525=501%:%
%:%526=502%:%
%:%527=503%:%
%:%528=504%:%
%:%529=505%:%
%:%530=506%:%
%:%531=507%:%
%:%532=508%:%
%:%533=509%:%
%:%534=510%:%
%:%535=511%:%
%:%536=512%:%
%:%537=513%:%
%:%538=514%:%
%:%539=515%:%
%:%540=516%:%
%:%541=517%:%
%:%550=524%:%
%:%562=530%:%
%:%563=531%:%
%:%564=532%:%
%:%565=533%:%
%:%566=534%:%
%:%567=535%:%
%:%568=536%:%
%:%569=537%:%
%:%570=538%:%
%:%571=539%:%
%:%572=540%:%
%:%573=541%:%
%:%574=542%:%
%:%575=543%:%
%:%576=544%:%
%:%577=545%:%
%:%586=558%:%
%:%598=560%:%
%:%599=561%:%
%:%600=562%:%
%:%604=568%:%
%:%608=570%:%
%:%609=571%:%
%:%610=572%:%
%:%611=573%:%
%:%612=574%:%
%:%613=575%:%
%:%614=576%:%
%:%618=579%:%
%:%622=585%:%
%:%623=586%:%
%:%624=587%:%
%:%625=588%:%
%:%625=589%:%
%:%626=590%:%
%:%627=591%:%
%:%628=592%:%
%:%629=593%:%
%:%630=594%:%
%:%631=595%:%
%:%632=596%:%
%:%633=597%:%
%:%634=598%:%
%:%635=599%:%
%:%636=600%:%
%:%636=601%:%
%:%637=602%:%
%:%638=603%:%
%:%639=604%:%
%:%640=605%:%
%:%641=606%:%
%:%642=607%:%
%:%643=608%:%
%:%644=609%:%
%:%645=610%:%
%:%646=611%:%
%:%647=612%:%
%:%648=613%:%
%:%649=614%:%
%:%650=615%:%
%:%651=616%:%
%:%652=617%:%
%:%653=618%:%
%:%654=619%:%
%:%655=620%:%
%:%655=621%:%
%:%656=622%:%
%:%657=623%:%
%:%658=624%:%
%:%659=625%:%
%:%660=626%:%
%:%661=627%:%
%:%662=628%:%
%:%663=629%:%
%:%664=630%:%
%:%664=631%:%
%:%665=632%:%
%:%669=636%:%
%:%673=638%:%
%:%674=639%:%
%:%675=640%:%
%:%676=641%:%
%:%677=642%:%
%:%678=643%:%
%:%679=644%:%
%:%680=645%:%
%:%681=646%:%
%:%682=647%:%
%:%683=648%:%
%:%684=649%:%
%:%685=650%:%
%:%689=652%:%
%:%693=659%:%
%:%697=661%:%
%:%697=662%:%
%:%698=663%:%
%:%699=664%:%
%:%700=665%:%
%:%701=666%:%
%:%702=667%:%
%:%703=668%:%
%:%704=669%:%
%:%705=670%:%
%:%706=671%:%
%:%707=672%:%
%:%708=673%:%
%:%709=674%:%
%:%710=675%:%
%:%711=676%:%
%:%712=677%:%
%:%713=678%:%
%:%714=679%:%
%:%715=680%:%
%:%716=681%:%
%:%717=682%:%
%:%717=683%:%
%:%718=684%:%
%:%719=685%:%
%:%728=687%:%
%:%740=689%:%
%:%741=690%:%
%:%742=691%:%
%:%743=692%:%
%:%744=693%:%
%:%745=694%:%
%:%749=696%:%
%:%750=697%:%
%:%751=698%:%
%:%753=700%:%
%:%754=701%:%
%:%755=702%:%
%:%756=703%:%
%:%758=705%:%
%:%759=706%:%
%:%760=707%:%
%:%761=708%:%
%:%762=709%:%
%:%762=710%:%
%:%763=711%:%
%:%768=715%:%
%:%769=716%:%
%:%770=717%:%
%:%771=718%:%
%:%772=719%:%
%:%776=765%:%
%:%780=767%:%
%:%780=768%:%
%:%781=769%:%
%:%782=770%:%
%:%783=771%:%
%:%784=772%:%
%:%788=774%:%
%:%789=775%:%
%:%790=776%:%
%:%791=777%:%
%:%792=778%:%
%:%793=779%:%
%:%794=780%:%
%:%795=781%:%
%:%796=782%:%
%:%797=783%:%
%:%798=784%:%
%:%799=785%:%
%:%800=786%:%
%:%801=787%:%
%:%802=788%:%
%:%803=789%:%
%:%807=791%:%
%:%808=792%:%
%:%809=793%:%
%:%810=794%:%
%:%811=795%:%
%:%812=796%:%
%:%813=797%:%
%:%814=798%:%
%:%815=799%:%
%:%816=800%:%
%:%817=801%:%
%:%818=802%:%
%:%819=803%:%
%:%820=804%:%
%:%821=805%:%
%:%825=815%:%
%:%829=817%:%
%:%830=818%:%
%:%834=819%:%
%:%835=820%:%
%:%837=821%:%
%:%838=822%:%
%:%843=824%:%
%:%844=825%:%
%:%845=826%:%
%:%846=827%:%
%:%847=828%:%
%:%848=829%:%
%:%849=830%:%
%:%850=831%:%
%:%851=832%:%
%:%851=833%:%
%:%851=834%:%
%:%852=835%:%
%:%853=836%:%
%:%854=837%:%
%:%855=838%:%
%:%856=839%:%
%:%865=841%:%
%:%877=845%:%
%:%881=847%:%
%:%882=848%:%
%:%883=849%:%
%:%884=850%:%
%:%885=851%:%
%:%886=852%:%
%:%887=853%:%
%:%888=854%:%
%:%889=855%:%
%:%890=856%:%
%:%891=857%:%
%:%892=858%:%
%:%893=859%:%
%:%894=860%:%
%:%895=861%:%
%:%896=862%:%
%:%897=863%:%
%:%898=864%:%
%:%899=865%:%
%:%900=866%:%
%:%901=867%:%
%:%902=868%:%
%:%903=869%:%
%:%904=870%:%
%:%905=871%:%
%:%906=872%:%
%:%907=873%:%
%:%907=874%:%
%:%908=875%:%
%:%909=876%:%
%:%910=877%:%
%:%911=878%:%
%:%912=879%:%
%:%913=880%:%
%:%914=881%:%
%:%915=882%:%
%:%916=883%:%
%:%917=884%:%
%:%918=885%:%
%:%922=888%:%
%:%926=891%:%
%:%930=893%:%
%:%931=894%:%
%:%932=895%:%
%:%933=896%:%
%:%934=897%:%
%:%935=898%:%
%:%936=899%:%
%:%937=900%:%
%:%938=901%:%
%:%939=902%:%
%:%940=903%:%
%:%941=904%:%
%:%942=905%:%
%:%946=907%:%
%:%947=908%:%
%:%948=909%:%
%:%949=910%:%
%:%950=911%:%
%:%951=912%:%
%:%952=913%:%
%:%953=914%:%
%:%953=915%:%
%:%954=916%:%
%:%955=917%:%
%:%956=918%:%
%:%957=919%:%
%:%958=920%:%
%:%959=921%:%
%:%959=922%:%
%:%960=923%:%
%:%961=924%:%
%:%962=925%:%
%:%966=928%:%
%:%970=930%:%
%:%971=931%:%
%:%972=932%:%
%:%973=933%:%
%:%974=934%:%
%:%975=935%:%
%:%976=936%:%
%:%977=937%:%
%:%978=938%:%
%:%979=939%:%
%:%980=940%:%
%:%981=941%:%
%:%985=943%:%
%:%986=944%:%
%:%987=945%:%
%:%988=946%:%
%:%989=947%:%
%:%990=948%:%
%:%991=949%:%
%:%992=950%:%
%:%993=951%:%
%:%994=952%:%
%:%995=953%:%
%:%996=954%:%
%:%997=955%:%
%:%997=956%:%
%:%998=957%:%
%:%999=958%:%
%:%1000=959%:%
%:%1001=960%:%
%:%1002=961%:%
%:%1003=962%:%
%:%1004=963%:%
%:%1005=964%:%
%:%1006=965%:%
%:%1007=966%:%
%:%1008=967%:%
%:%1009=968%:%
%:%1010=969%:%
%:%1011=970%:%
%:%1012=971%:%
%:%1013=972%:%
%:%1014=973%:%
%:%1015=974%:%
%:%1015=975%:%
%:%1016=976%:%
%:%1017=977%:%
%:%1018=978%:%
%:%1019=979%:%
%:%1020=980%:%
%:%1021=981%:%
%:%1022=982%:%
%:%1022=983%:%
%:%1026=985%:%
%:%1027=986%:%
%:%1028=987%:%
%:%1029=988%:%
%:%1030=989%:%
%:%1031=990%:%
%:%1032=991%:%
%:%1033=992%:%
%:%1034=993%:%
%:%1035=994%:%
%:%1036=995%:%
%:%1037=996%:%
%:%1038=997%:%
%:%1039=998%:%
%:%1040=999%:%
%:%1041=1000%:%
%:%1042=1001%:%
%:%1046=1005%:%
%:%1050=1009%:%
%:%1054=1015%:%
%:%1055=1016%:%
%:%1056=1017%:%
%:%1057=1018%:%
%:%1058=1019%:%
%:%1059=1020%:%
%:%1060=1021%:%
%:%1061=1022%:%
%:%1062=1023%:%
%:%1063=1024%:%
%:%1064=1025%:%
%:%1065=1026%:%
%:%1066=1027%:%
%:%1067=1028%:%
%:%1068=1029%:%
%:%1069=1030%:%
%:%1070=1031%:%
%:%1071=1032%:%
%:%1072=1033%:%
%:%1073=1034%:%
%:%1074=1035%:%
%:%1075=1036%:%
%:%1076=1037%:%
%:%1077=1038%:%
%:%1078=1039%:%
%:%1079=1040%:%
%:%1080=1041%:%
%:%1081=1042%:%
%:%1082=1043%:%
%:%1083=1044%:%
%:%1084=1045%:%
%:%1085=1046%:%
%:%1086=1047%:%
%:%1087=1048%:%
%:%1088=1049%:%
%:%1089=1050%:%
%:%1090=1051%:%
%:%1091=1052%:%
%:%1092=1053%:%
%:%1093=1054%:%
%:%1094=1055%:%
%:%1095=1056%:%
%:%1096=1057%:%
%:%1097=1058%:%
%:%1098=1059%:%
%:%1099=1060%:%
%:%1099=1061%:%
%:%1100=1062%:%
%:%1101=1063%:%
%:%1105=1092%:%
%:%1109=1093%:%
%:%1110=1094%:%
%:%1111=1095%:%
%:%1112=1096%:%
%:%1112=1097%:%
%:%1113=1098%:%
%:%1114=1099%:%
%:%1115=1100%:%
%:%1116=1101%:%
%:%1117=1102%:%
%:%1117=1103%:%
%:%1118=1104%:%
%:%1122=1108%:%
%:%1123=1109%:%
%:%1124=1110%:%
%:%1125=1111%:%
%:%1126=1112%:%
%:%1127=1113%:%
%:%1128=1114%:%
%:%1129=1115%:%
%:%1130=1116%:%
%:%1131=1117%:%
%:%1132=1118%:%
%:%1133=1119%:%
%:%1134=1120%:%
%:%1135=1121%:%
%:%1136=1122%:%
%:%1137=1123%:%
%:%1138=1124%:%
%:%1139=1125%:%
%:%1140=1126%:%
%:%1141=1127%:%
%:%1142=1128%:%
%:%1143=1129%:%
%:%1144=1130%:%
%:%1145=1131%:%
%:%1146=1132%:%
%:%1147=1133%:%
%:%1151=1138%:%
%:%1155=1141%:%
%:%1156=1142%:%
%:%1157=1143%:%
%:%1158=1144%:%
%:%1162=1148%:%
%:%1166=1150%:%
%:%1167=1151%:%
%:%1168=1152%:%
%:%1169=1153%:%
%:%1169=1154%:%
%:%1170=1155%:%
%:%1171=1156%:%
%:%1172=1157%:%
%:%1173=1158%:%
%:%1177=1161%:%
%:%1178=1162%:%
%:%1179=1163%:%
%:%1180=1164%:%
%:%1181=1165%:%
%:%1182=1166%:%
%:%1183=1167%:%
%:%1184=1168%:%
%:%1185=1169%:%
%:%1186=1170%:%
%:%1187=1171%:%
%:%1188=1172%:%
%:%1189=1173%:%
%:%1190=1174%:%
%:%1191=1175%:%
%:%1192=1176%:%
%:%1193=1177%:%
%:%1194=1178%:%
%:%1195=1179%:%
%:%1196=1180%:%
%:%1197=1181%:%
%:%1198=1182%:%
%:%1199=1183%:%
%:%1203=1185%:%
%:%1204=1186%:%
%:%1205=1187%:%
%:%1206=1188%:%
%:%1207=1189%:%
%:%1208=1190%:%
%:%1209=1191%:%
%:%1210=1192%:%
%:%1211=1193%:%
%:%1212=1194%:%
%:%1213=1195%:%
%:%1214=1196%:%
%:%1215=1197%:%
%:%1216=1198%:%
%:%1217=1199%:%
%:%1218=1200%:%
%:%1219=1201%:%
%:%1220=1202%:%
%:%1221=1203%:%
%:%1225=1206%:%
%:%1229=1208%:%
%:%1229=1209%:%
%:%1230=1210%:%
%:%1231=1211%:%
%:%1232=1212%:%
%:%1233=1213%:%
%:%1234=1214%:%
%:%1235=1215%:%
%:%1236=1216%:%
%:%1237=1217%:%
%:%1241=1219%:%
%:%1245=1220%:%
%:%1246=1221%:%
%:%1247=1222%:%
%:%1248=1223%:%
%:%1249=1224%:%
%:%1250=1225%:%
%:%1251=1226%:%
%:%1252=1227%:%
%:%1253=1228%:%
%:%1254=1229%:%
%:%1255=1230%:%
%:%1256=1231%:%
%:%1257=1232%:%
%:%1258=1233%:%
%:%1259=1234%:%
%:%1260=1235%:%
%:%1261=1236%:%
%:%1262=1237%:%
%:%1263=1238%:%
%:%1264=1239%:%
%:%1265=1240%:%
%:%1268=1243%:%
%:%1269=1244%:%
%:%1270=1245%:%
%:%1271=1246%:%
%:%1272=1247%:%
%:%1273=1248%:%
%:%1276=1259%:%
%:%1285=1261%:%
%:%1297=1263%:%
%:%1297=1264%:%
%:%1301=1265%:%
%:%1302=1266%:%
%:%1304=1267%:%
%:%1305=1268%:%
%:%1310=1271%:%
%:%1311=1272%:%
%:%1312=1273%:%
%:%1313=1274%:%
%:%1314=1275%:%
%:%1315=1276%:%
%:%1316=1277%:%
%:%1317=1278%:%
%:%1318=1279%:%
%:%1318=1280%:%
%:%1319=1281%:%
%:%1320=1282%:%
%:%1321=1283%:%
%:%1322=1284%:%
%:%1323=1285%:%
%:%1324=1286%:%
%:%1325=1287%:%
%:%1334=1289%:%
%:%1346=1291%:%
%:%1347=1292%:%
%:%1348=1293%:%
%:%1349=1294%:%
%:%1350=1295%:%
%:%1351=1296%:%
%:%1352=1297%:%
%:%1353=1298%:%
%:%1353=1299%:%
%:%1354=1300%:%
%:%1355=1301%:%
%:%1356=1302%:%
%:%1357=1303%:%
%:%1358=1304%:%
%:%1359=1305%:%
%:%1360=1306%:%
%:%1361=1307%:%
%:%1362=1308%:%
%:%1363=1309%:%
%:%1364=1310%:%
%:%1365=1311%:%
%:%1366=1312%:%
%:%1367=1313%:%
%:%1368=1314%:%
%:%1369=1315%:%
%:%1370=1316%:%
%:%1371=1317%:%
%:%1372=1318%:%
%:%1373=1319%:%
%:%1374=1320%:%
%:%1375=1321%:%
%:%1376=1322%:%
%:%1377=1323%:%
%:%1378=1324%:%
%:%1379=1325%:%
%:%1380=1326%:%
%:%1381=1327%:%
%:%1382=1328%:%
%:%1386=1331%:%
%:%1390=1333%:%
%:%1391=1334%:%
%:%1392=1335%:%
%:%1393=1336%:%
%:%1394=1337%:%
%:%1395=1338%:%
%:%1396=1339%:%
%:%1397=1340%:%
%:%1398=1341%:%
%:%1399=1342%:%
%:%1400=1343%:%
%:%1401=1344%:%
%:%1402=1345%:%
%:%1403=1346%:%
%:%1404=1347%:%
%:%1405=1348%:%
%:%1406=1349%:%
%:%1407=1350%:%
%:%1408=1351%:%
%:%1409=1352%:%
%:%1410=1353%:%
%:%1411=1354%:%
%:%1412=1355%:%
%:%1413=1356%:%
%:%1414=1357%:%
%:%1415=1358%:%
%:%1416=1359%:%
%:%1417=1360%:%
%:%1418=1361%:%
%:%1419=1362%:%
%:%1420=1363%:%
%:%1421=1364%:%
%:%1422=1365%:%
%:%1423=1366%:%
%:%1424=1367%:%
%:%1425=1368%:%
%:%1426=1369%:%
%:%1427=1370%:%
%:%1428=1371%:%
%:%1429=1372%:%
%:%1430=1373%:%
%:%1431=1374%:%
%:%1432=1375%:%
%:%1433=1376%:%
%:%1434=1377%:%
%:%1435=1378%:%
%:%1436=1379%:%
%:%1437=1380%:%
%:%1438=1381%:%
%:%1439=1382%:%
%:%1440=1383%:%
%:%1441=1384%:%
%:%1442=1385%:%
%:%1443=1386%:%
%:%1444=1387%:%
%:%1445=1388%:%
%:%1446=1389%:%
%:%1447=1390%:%
%:%1448=1391%:%
%:%1449=1392%:%
%:%1450=1393%:%
%:%1451=1394%:%
%:%1452=1395%:%
%:%1453=1396%:%
%:%1454=1397%:%
%:%1455=1398%:%
%:%1456=1399%:%
%:%1457=1400%:%
%:%1458=1401%:%
%:%1459=1402%:%
%:%1460=1403%:%
%:%1461=1404%:%
%:%1462=1405%:%
%:%1463=1406%:%
%:%1464=1407%:%
%:%1465=1408%:%
%:%1466=1409%:%
%:%1467=1410%:%
%:%1468=1411%:%
%:%1469=1412%:%
%:%1470=1413%:%
%:%1471=1414%:%
%:%1472=1415%:%
%:%1473=1416%:%
%:%1474=1417%:%
%:%1475=1418%:%
%:%1476=1419%:%
%:%1477=1420%:%
%:%1478=1421%:%
%:%1479=1422%:%
%:%1480=1423%:%
%:%1481=1424%:%
%:%1482=1425%:%
%:%1483=1426%:%
%:%1484=1427%:%
%:%1485=1428%:%
%:%1486=1429%:%
%:%1487=1430%:%
%:%1488=1431%:%
%:%1489=1432%:%
%:%1490=1433%:%
%:%1491=1434%:%
%:%1492=1435%:%
%:%1493=1436%:%
%:%1494=1437%:%
%:%1495=1438%:%
%:%1496=1439%:%
%:%1497=1440%:%
%:%1498=1441%:%
%:%1499=1442%:%
%:%1500=1443%:%
%:%1501=1444%:%
%:%1502=1445%:%
%:%1503=1446%:%
%:%1504=1447%:%
%:%1505=1448%:%
%:%1506=1449%:%
%:%1507=1450%:%
%:%1508=1451%:%
%:%1509=1452%:%
%:%1510=1453%:%
%:%1511=1454%:%
%:%1512=1455%:%
%:%1513=1456%:%
%:%1514=1457%:%
%:%1515=1458%:%
%:%1516=1459%:%
%:%1517=1460%:%
%:%1518=1461%:%
%:%1519=1462%:%
%:%1520=1463%:%
%:%1521=1464%:%
%:%1522=1465%:%
%:%1523=1466%:%
%:%1524=1467%:%
%:%1525=1468%:%
%:%1526=1469%:%
%:%1527=1470%:%
%:%1528=1471%:%
%:%1529=1472%:%
%:%1530=1473%:%
%:%1531=1474%:%
%:%1532=1475%:%
%:%1533=1476%:%
%:%1534=1477%:%
%:%1535=1478%:%
%:%1536=1479%:%
%:%1537=1480%:%
%:%1538=1481%:%
%:%1539=1482%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimML
%
\endisadelimML
%
\isatagML
%
\endisatagML
{\isafoldML}%
%
\isadelimML
%
\endisadelimML
%
\begin{isamarkuptitle*}%
[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Isabelle/C%
\end{isamarkuptitle*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {abs},type = {scholarly_paper.abstract}, args={label = {abs},type = {scholarly_paper.abstract}, scholarly_paper.abstract.keywordlist = {{User Interface, Integrated Development, Program Verification, Shallow Embedding}}}]We present a framework for C code in C11 syntax deeply integrated into the Isabelle/PIDE
  development environment. Our framework provides an abstract interface for verification back-ends
  to be plugged-in independently. Thus, various techniques such as deductive program verification or
  white-box testing can be applied to the same source, which is part of an integrated PIDE document
  model. Semantic back-ends are free to choose the supported C fragment and its semantics. In
  particular, they can differ on the chosen memory model or the specification mechanism
  for framing conditions.

@@

### 2019-10-15 C11-FrontEnd/document/preamble.tex
simplify
synchronize with fortesse revision 5366

%e% This is a placeholder for user-specific configuration and packages.
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage[en-US]{datetime2}      % For \DTMdate, etc.
\usepackage{amssymb}
\usepackage{listings}
\usepackage{lstisadof}
\usepackage{xspace}
\usepackage[draft]{fixme}
\usepackage{wrapfig}

\title{Deeply Integrating C11 Code Support into Isabelle/PIDE} % should be auto-generated
\addauthor{Frédéric Tuong\inst {1}} % should be auto-generated

>>>>

%e% This is a placeholder for user-specific configuration and packages.
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage[en-US]{datetime2}      % For \DTMdate, etc.
\usepackage{amssymb}
\usepackage{listings}
\usepackage{lstisadof}
\usepackage{xspace}
\usepackage[draft]{fixme}
\usepackage{wrapfig}

\title{} % should be auto-generated
\addauthor{\href{https://www.lri.fr/~ftuong/}{Frédéric Tuong}\inst{1} \and \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}\inst{1}} % should be auto-generated
